\documentclass[twoside]{article}
\usepackage[a4paper,includeall,bindingoffset=0cm,margin=2cm,
	            marginparsep=0cm,marginparwidth=0cm]{geometry}
\addtolength{\textheight}{-1cm}
\usepackage[english]{babel}
\usepackage[babel=true]{csquotes}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage[]{fancyhdr}
\pagestyle{fancy}
\setlength{\headheight}{50pt}
\setlength{\headsep}{40pt}
\fancyhead{}
%\lhead[\thesection]{\hspace{10pt}}
\fancyhead[RO]{\rightmark}
\fancyhead[LE]{\leftmark}
%\usepackage{amssymb}
%\renewcommand{\oddsidemargin}{}
%\renewcommand{\evensidemargin}{62pt}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[]{algorithm2e}


\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	breaklinks=true,
	linkcolor=blue,
	urlcolor=blue}
\newtheorem{thdef}{Definition}
\theoremstyle{remark}
\newtheorem{rk}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\thref}[2]{\hyperref[#2]{#1 \ref*{#2}}}
\numberwithin{equation}{subsection}

\usepackage{url}
\usepackage[]{xcolor}
\definecolor{light-gray}{gray}{0.6}
\definecolor{blue}{RGB}{0,0,153}
\definecolor{blue1}{RGB}{0,102,204}
\definecolor{blue2}{RGB}{51,153,255}
\definecolor{blue3}{RGB}{0,153,153}
\definecolor{blue4}{RGB}{102,102,255}
\definecolor{red1}{RGB}{255,0,0}
\definecolor{orange1}{RGB}{255,153,51}
\definecolor{green}{RGB}{0,204,0}
\definecolor{purple}{RGB}{204,0,204}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{boxedminipage}
\usepackage{tikz}
\usetikzlibrary{calc} 

\setcounter{MaxMatrixCols}{20}

\tikzset{
  x=1ex,y=1ex,
  hwblock/.style={draw, rectangle, rounded corners=.3, very thick, fill=black!5, font=\sf, minimum height=5ex},
  hwbus/.style={very thick,>=stealth},
  hwwire/.style={thin, >=stealth, },
  hwword/.style={draw, rectangle, minimum height=3ex},
  bitwidth/.style={font=\scriptsize,midway,right}
}

\newcommand{\msbout}{m_{\text{out}}}
\newcommand{\appr}[1]{\widetilde{#1}}
\newcommand{\yout}{\widetilde{y}_{\text{out}}}
\newcommand{\abserr}{\varepsilon}
\newcommand{\epssopc}{\abserr_{\text{r}}}
\newcommand{\epsfinalround}{\abserr_{\text{f}}}
\newcommand{\TODO}{\textbf{TODO}}

\title{Architecture synthesis for linear time-invariant filters}
\author{Antoine Martinet}

\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage

\section*{ Introduction }
	\addcontentsline{toc}{section}{Introduction}

	Filters are nowadays essential tools for designing responsive systems.
	%As they appear in both signal processing and command communities,
	In signal processing, filters are used in
	radio signal coding and decoding, image and sound processing, and so on.
	In addition, they are also used in many control applications.


%	Although most of all the potential filters can be computed in software,
%	some interesting applications in hardware could help to accelerate such computations, 

	For most applications, filters can be computed in software.
	However, for performance reasons hardware implementations are needed in many applications.
	There is an interest in FPGAs implementations because they can help for prototyping a software defined radio (SDR).
	%interest on applications FPGAs implementations because help for prototyping software defined radio. SDR is the main researche subjevt of the SOCRATE team 
	%\TODO: make a sentence with comment above

	
	SDR is the main research subject of the SOCRATE team, at the CITI lab, where this work has been conducted.
	The goal of this internship was to design a parametric architecture generator for Linear Time Invariant (LTI) filters.
	This work has been integrated to FloPoCo tool,
	whose purpose is to generate architecture cores for computing just right.


	This report first presents the context of LTI filters, SIF and their implementation in part \ref{Part1}.
	Then we will describe the details of our implementation in arbitrary precision in part \ref{Part2}.
	Finally, an overview of the future work will be presented in part \ref{Part3}.

\section{Tools for expressing filters and signal processing}
\label{Part1}
\input{firstPart}

\newpage
\section{Implementation}
\label{Part2}
\input{secondPart}

\newpage
\section{Further work}
\label{Part3}
\input{thirdPart}

\section*{Conclusion}
	\addcontentsline{toc}{section}{Conclusion}
	In this work, I tried to give an overview of LTI filters, and the considerations to take into account when trying to implement them.
	I tried to adapt concepts and calculation from Lopez's and Hilaire's work to the context of generating architectures computing just right.
	This context is merging ideas from the communities of automatic, signal, and computer arithmetics, so there was a part of unification in notations and conventions.
	Finally, I began the implementation of a parametric definition in the FloPoCo framework.
	This was permitted through the definition of a specification language and the integration of external code from LIP6.
	Further work will take into account many improvements and optimizations, such as:
	\begin{itemize}
		\item static analysis on coefficients
		\item sub-filter detection
		\item bounds and precision computation improvements
		\item format re-specification
	\end{itemize}

\bibliographystyle{plain}
\bibliography{report}  % main.bib is the name of the Bibliography in this case
\newpage
\section*{Appendix: Notations and reminders about signal processing}
	\addcontentsline{toc}{section}{Appendix: Notations and reminders about signal processing}
\input{annexes}
%\TODO: talk about code: part title: "Implementation" (not in appendix)
%\TODO: One entries-> powers of two
%\TODO: Optimality of realization not discussed by me but by LIP6 + figure
\end{document}

