\documentclass[twoside]{article}
%\usepackage[a4paper,includeall,bindingoffset=0cm,margin=2cm,
%	            marginparsep=0cm,marginparwidth=0cm]{geometry}
\usepackage[a4paper,includeall]{geometry}
%\addtolength{\textheight}{-1cm}
\usepackage[english]{babel}
\usepackage[babel=true]{csquotes}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage[]{fancyhdr}
%\pagestyle{fancy}
%\setlength{\headheight}{50pt}
%\setlength{\headsep}{40pt}
%\fancyhead{}
%\lhead[\thesection]{\hspace{10pt}}
%\fancyhead[RO]{\rightmark}
%\fancyhead[LE]{\leftmark}
%\usepackage{amssymb}
%\setlength{\oddsidemargin}{1.575in}
%\setlength{\evensidemargin}{1.575in}
\setlength{\oddsidemargin}{1.18in}
\setlength{\hoffset}{-1in}
\setlength{\textwidth}{5.91in}
\setlength{\evensidemargin}{1.18in}
\setlength{\marginparwidth}{0pt}
\setlength{\marginparsep}{0pt}

\setlength{\topmargin}{1.18in}
\setlength{\voffset}{-1in}
\setlength{\textheight}{8.40in}

\pagenumbering{gobble} %TODO: uncomment this at the end of development

\usepackage[toc,page]{appendix}

\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[]{algorithm2e}


\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	breaklinks=true,
	linkcolor=blue,
	urlcolor=blue}
\newtheorem{thdef}{Definition}
\theoremstyle{remark}
\newtheorem{rk}{Remark}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newcommand{\thref}[2]{\hyperref[#2]{#1 \ref*{#2}}}
\numberwithin{equation}{subsection}

\usepackage{url}
\usepackage[]{xcolor}
\definecolor{light-gray}{gray}{0.6}
\definecolor{blue}{RGB}{0,0,153}
\definecolor{blue1}{RGB}{0,102,204}
\definecolor{blue2}{RGB}{51,153,255}
\definecolor{blue3}{RGB}{0,153,153}
\definecolor{blue4}{RGB}{102,102,255}
\definecolor{red1}{RGB}{255,0,0}
\definecolor{orange1}{RGB}{255,153,51}
\definecolor{green}{RGB}{0,204,0}
\definecolor{purple}{RGB}{204,0,204}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{boxedminipage}
\usepackage{tikz}
\usetikzlibrary{calc} 

\setcounter{MaxMatrixCols}{20}

\tikzset{
  x=1ex,y=1ex,
  hwblock/.style={draw, rectangle, rounded corners=.3, very thick, fill=black!5, font=\sf, minimum height=5ex},
  hwbus/.style={very thick,>=stealth},
  hwwire/.style={thin, >=stealth, },
  hwword/.style={draw, rectangle, minimum height=3ex},
  bitwidth/.style={font=\scriptsize,midway,right}
}

\newcommand{\msbout}{m_{\text{out}}}
\newcommand{\appr}[1]{\widetilde{#1}}
\newcommand{\yout}{\widetilde{y}_{\text{out}}}
\newcommand{\abserr}{\varepsilon}
\newcommand{\epssopc}{\abserr_{\text{r}}}
\newcommand{\epsfinalround}{\abserr_{\text{f}}}
\newcommand{\TODO}{\textbf{TODO}}

\title{\vspace{-40pt}
	\fontsize{14}{16.8}\selectfont
	\textbf{Architecture synthesis for linear time-invariant filters}}
\author{\\ \fontsize{10}{12}\selectfont Antoine Martinet \\\\ \fontsize{9}{10.8}\selectfont Département Informatique \\ \fontsize{9}{10.8}\selectfont INSA de Lyon \\ \fontsize{9}{10.8}\selectfont 2014/2015}
%\date{2 February - 31 Jully, \\ \vspace{5pt} 2015}
\date{}

\begin{document}

\maketitle
%\tableofcontents
\noindent Under the responsability of : \\
Florent de Dinechin : INRIA Rhône-Alpes \\
Florent de Dinechin : Département Informatique
\vspace{20pt}

\begingroup

	\fontsize{9}{10.8}\selectfont
	\leftskip0.395in
	\rightskip\leftskip
	\noindent \textbf{Abstract.}
	The literature offers papers comparing different realizations of the same filter,
	and observing that more accuracy can be obtained at the expense of more multipliers.
	Such studies are relevant in software implementations, where the multiplier size is a given.
	In the context of hardware or FPGA implementations, more accuracy can also be bought by larger multipliers.
	This internship will study this trade-off and design tools that explore it.
	The ultimate objective is to generate the smallest or fastest filter satisfying a given accuracy specification.

	\vspace{20pt}

\endgroup
	
	\noindent \textbf{Key-words:}
	signal processing,
	architecture generation,
	LTI Filters.


\section{ Introduction }
	%\addcontentsline{toc}{section}{Introduction}

	Filters are nowadays essential tools for designing responsive systems.
	%As they appear in both signal processing and command communities,
	In signal processing, filters are used in
	radio signal coding and decoding, image and sound processing, and so on.
	In addition, they are also used in many control applications.


%	Although most of all the potential filters can be computed in software,
%	some interesting applications in hardware could help to accelerate such computations, 

	For most applications, filters can be computed in software.
	However, for performance reasons hardware implementations are needed in many cases.
	There is an interest in FPGAs implementations because they can help for prototyping a software defined radio (SDR).
	%interest on applications FPGAs implementations because help for prototyping software defined radio. SDR is the main researche subjevt of the SOCRATE team 
	%\TODO: make a sentence with comment above

	
	SDR is the main research subject of the SOCRATE team, at the CITI lab, where this work has been conducted.
	The goal of this internship was to design a parametric architecture generator for Linear Time Invariant (LTI) filters.
	This work has been integrated to FloPoCo tool,
	whose purpose is to generate architecture cores computing just right.


	This report first presents the context of LTI filters, SIF and their implementation in part \ref{Part1}.
	Part \ref{Part2} will then describe the details of the implementation brought in arbitrary precision.
	Finally, an overview of the future work will be presented in part \ref{Part3}.

\section{Tools for expressing filters and signal processing}
\label{Part1}
\input{firstPart}

%\newpage
\section{Architecture generation}
\label{Part2}
\input{secondPart}

%\newpage
\section{Further work}
\label{Part3}
\input{thirdPart}

%\newpage
\section*{Conclusion}
	\addcontentsline{toc}{section}{Conclusion}
	This work tried to give an overview of LTI filters, and the considerations to take into account when trying to implement them.
	This report tried to adapt concepts and calculations from Lopez's and Hilaire's work to the context of generating architectures computing just right.
	This context is merging ideas from the communities of automatic, signal, and computer arithmetics, so a certain amount of time was spent on the unification of notations and conventions.
	Finally, the implementation of a parametric definition in the FloPoCo framework was started.
	This was permitted through the definition of a specification format and the integration of external code from LIP6.
	Further work will take into account many improvements and optimizations, such as:
	\begin{itemize}
		\item power of two removing
		\item sub-filter detection
		\item bounds and precision computation improvements
		\item format re-specification
	\end{itemize}

\bibliographystyle{plain}
\bibliography{report}  % main.bib is the name of the Bibliography in this case
\newpage
\begin{appendices}
\section{Notations and reminders about signal processing}
	%\addcontentsline{toc}{section}{Appendix: Notations and reminders about signal processing}
\input{annexes}
\section{Table of contents}
\tableofcontents
\end{appendices}
%\TODO: talk about code: part title: "Implementation" (not in appendix)
\end{document}

